\documentclass[11pt,line,margin]{resume}
 
\usepackage[latin1]{inputenc}
\usepackage[english,french]{babel}
\usepackage[T1]{fontenc}
\usepackage{fontawesome}
\usepackage{graphicx,wrapfig}
\usepackage{url}
\usepackage[colorlinks=true, pdfstartview=FitV, linkcolor=black, citecolor=black, urlcolor=black]{hyperref}
\usepackage{textcomp}
\usepackage{times}
\pdfcompresslevel=9
\edef\hc{\string:}
\newcommand{\eg}{{\it e.g.}}
\begin{document}{\sc \Large Fereshteh Forghani}
\begin{resume}


% === PERSONAL INFO ===
 \section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{3in}}
\faEnvelopeSquare \space fereshteh.forghani2012@gmail.com 	&  \faGlobe  \space \href{https://fereshtehforghani.netlify.app/}{Personal Website}\\
 \faLinkedinSquare \space \href{https://www.linkedin.com/in/fereshteh-forghani-aa76b8173/}{https://www.linkedin.com/in/fereshtehforghani} 	 &  \faPhoneSquare \space +98 913 518 9067  \\
 \\     
\end{tabular}

% === OBJECTIVE ===

    % \section{}A Machine Learning applied researcher with practical industry experience implementing algorithms in production software environment.
 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-0.2in}
\section{\sc Research Interests}

%{Machine Learning, Deep Learning, Computer Vision, Medical Image Analysis, Artificial Intelligence }
{Machine Learning, Deep Learning, Computer Vision, Medical Image Analysis, \\Natural Language Processing,  Artificial Intelligence }

%\vspace{-0.17in}
%\section{\sc Computer \\ Skills}
%\begin{list2}
%\item Programming: C/C++, Python, CUDA
%\item Data Manipulation: Pandas, SQL
%\item Vision/ML Libraries: TensorFlow, PyTorch, Scikit-Learn, OpenCV
%\item Efficient Data Storage: Apache Parquet
%\item Distributed Data Processing: Apache Beam, Petastorm
%\end{list2}

%\vspace{-0.2in}
\section{\sc Education}
\begin{list1}
\item[] {\bf \href{http://www.sharif.ir/home}{Sharif University of Technology}}, Tehran, Iran\\
B.S. in Computer Engineering  \hfill\textit{2017-present}\\
Major GPA: {\bf 19.45}/20 , GPA till now: {\bf 18.53}/20  ({\bf 3.96}/4)\\ 
\textit{Bacholar Thesis}:
\par \setlength{\leftskip}{1cm} Cell Segmentation in Microscopic Images using Self-supervised Learning Methods 
\\
\par
\setlength{\leftskip}{0pt}
\textit{Coursework}: 
\par \setlength{\leftskip}{1cm}Machine Learning (20/20), Artificial Intelligence (19.9/20), Modern Information Retrieval (18.7/20), Probability and Statistics (18.6/20), Linear algebra (19.5/20), Signal processing (19.1/20), Data Structures and Algorithms (18.3/20), Advanced Programming (20/20)
\\
\par
\setlength{\leftskip}{0pt}

\item[] \textbf{Farzanegan High School}, National Organization for Development of Exceptional Talents(\href{https://en.wikipedia.org/wiki/National_Organization_for_Development_of_Exceptional_Talents}{Nodet}), Iran\\
Diploma in Mathematics and Physics  \hfill\textit{2013 - 2017}\\
GPA: {\bf 19.90}/20
\end{list1}

\vspace{-0.13in}
\section{\sc Research Experience}

\begin{list1}
\item[] \textbf{Internship at Ecole Polytechnique Federale de Lausanne (EPFL)} \\
Advised by Prof. A. Alahi, Visual Intelligence for Transportation (\href{https://www.epfl.ch/labs/vita/}{VITA}) Lab\hfill \textit{Jul 2021-present}\\ 
Used density estimation techniques such as \href{https://arxiv.org/abs/1705.07057}{Masked autoregressive flow}, \href{https://arxiv.org/abs/1605.08803}{RealNVP} and \href{https://arxiv.org/abs/1502.03509}{Masked autoencoder for distribution estimation} to find natural adversarial examples to test the reliability of human trajectory predictors .\\

\item[] \textbf{Research Assistant at Sharif University of Technology} \hfill \textit{Oct 2020-present}\\
\quad Advised by  Prof. Mohammad Hossein Rohban, Medical Image Analysis Group, Department of Computer Engineering \\
Used unsupervised learning frameworks (simCLR, MoCo, SimSiam) to train U-net encoder with unannotated cell images and improve IoU score after fine-tuning with annotated ones.\\

\item[] \textbf{Scientific Collaborator at Sharif University of Technology} \hfill\textit{May 2021 - September 2021}\\
\quad Advised by Prof. Shohreh Kasaei, Image Processing Lab (\href{http://ipl.ce.sharif.edu/}{IPL}), Department of Computer Engineering\\
Investigated adversarial attacks against Deep Neural Networks, specifically focusing on 3D point-cloud networks (PointNet) and various features learnt by their different layers.
\end{list1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%.  HONDA  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-0.14in}
\section{\sc Work Experience}
\begin{list1}
\item[] \textbf{Machine Learning Intern at  \href{https://sinaweb.net}{Sinaweb} Company} \hfill\textit{Summer 2020}\\
Worked on ML based forgery recognition (plagiarism  detection) in scientific articles through handwriting style recognition. \\
%\quad The aim of this project was to develop a plagiarism detection method. This method is
%using variations in writing style to identify potentially plagiarized passages.
\end{list1}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%   Academic Experience       %%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-0.2in}
\section{\sc Technical Skills}


\begin{list1}
\item[] \textbf {Languages and Tools\hc} 
%Python(Experienced in PyTorch, Tensorflow, Numpy, Pandas, NLTK), R, C/C++, Java, SQL, Git, Racket, MIPS32, Verilog
\begin {list2}
\item Programming\hc \space C/C++, Python, Java
\item Data Manipulation\hc \space Pandas, SQL
\item Vision/ML Libraries\hc ~ TensorFlow, PyTorch, Numpy, Scikit-Learn, NLTK, OpenCV
\item  Hardware\hc \space MIPS32, Verilog
\end{list2}
%\item[] \textbf{Software\hc}  Quartus, ModelSim, GEM5
\item[] \textbf{Web and Mobile app Development\hc}  Django, HTML, CSS, JS, Android, Swift
%\item Database: PostgreSQL, MySQL
\item[] \textbf{Operating Systems\hc}  Windows, Macintosh
%\item[] \textbf{Typesetting\hc}   \LaTeX, Microsoft Office
%\item Social skills: Teamwork,  Fast Learner,  Problem Solving, Creativity
\end{list1}
\newpage
\section{\sc Social Skills}
\begin{list1}
\item[] Teamwork,  Fast Learner,  Problem Solving, Creativity
\end{list1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%   Education.                %%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\item \textbf{35th place out of 300,000} competitors in \href{https://en.wikipedia.org/wiki/Iranian_University_Entrance_Exam}{National University Entrance Exam} of mathematics and physics , \textit{Summer 2017}\\
%Admission to Sharif University of Technology B.S. program
%\item \textbf{101st place out of 6,000} competitors in university entrance exam of English, \textit{Summer 2017}

		
% \vspace*{.05in}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%            %%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \newpage
\vspace{-0.05in}
\section{\sc University Projects} 
\begin{list2}
\item Cleaned data and trained models to find best clickthrough rate, Machine Learning Course Project (Python)  \hspace*{\fill}\mbox{\textit {Fall2020}}

\item Preprocessed, classified and clustered english Ted Talks and persian wikipedia pages in order to design an information retrieval system with search and query correction abilities, Modern Information Retrieval Course Project (Python) \hfill\textit{Fall 2020}
 \\
\href{https://github.com/mahtabbigverdi/Modern-Information-Retreival}{Project Github Link}
\item Food recipe provider app which provided recipes from Spoonacular api, Mobile programming Course Project (Android) \hfill\textit{Spring 2021} \\
\href{https://github.com/lilygoli/YumYum}{Project Github Link}
\item Appointment making website, System Analysis and Design Course Project (Django framework)  \hspace*{\fill}\mbox{\textit {Spring 2020}}
\\
\href{https://gitlab.com/AradMHM/sad-project}{Project Gitlab Link}
\item Farm frenzi game, Advance Programming Course Project (Java) \hfill\textit{Fall 2018}\\
\href{https://github.com/mdalirrooyfard/AP_7}{Project Github Link}
\item Pacman, Fundamenetals of Programming project Course Project (C) \hfill\textit{Fall 2017} \\
\href{https://github.com/sinaris76/96102104}{Project Github Link}
\end{list2}


\vspace{0.10in}
\section{\sc Honors and awards}
\begin{list2}
\item[] {\bf National University Entrance Exams (Konkur) }  \hfill {\textit
2017}\\
%\begin{list2}
			%\item[] 
			Ranked 125$^{th}$ among 150,000 in Mathematics and Physics. \\
			%\item[] 
			Ranked 101$^{th}$ among 6,500 in English Language. 
%\end{list2} 

\item[] {\bf Member of national ELITE foundation}\hfill\textit{2017 - Present} \\
Recipient of the Grant for Undergraduate Studies from the Iranian National Foundation of Elites. 

\item[] {\bf Recognized as talented student in entry exam of NODET} among students
for middle and high school. \hfill\textit{2010 and 2013}
\end{list2}


\vspace{-0.05in}
\section{\sc Teaching Experience} 
\begin{list2}
\item[] \textbf{Teaching Assistant} (Sharif University of Technology)
\begin{list2}
\item Machine Learning (graduate course), Dr. A. Hosseini \hfill\textit{Spring 2021 \& Fall 2021}
\item Artificial Intelligence, Dr. MH. Rohban \hfill\textit{Spring 2021}
\item Computer Architecture, Dr. H. Asadi \hfill\textit{Spring 2021}
\item Computer Structure and Language, Dr. L. Arshadi \hfill\textit{Fall 2020}
\item Digital Design, Dr. Sh. Hesabi \hfill\textit{Spring 2020}
\item Computer Structure and Language, Dr. H. Asadi \hfill\textit{Fall 2019}
\item Advance Programming, Dr. B. Hatami \hfill\textit{Spring 2019}
\end{list2}
\end{list2}

\vspace{-0.05in}
\section{\sc Volunteer Experience } 
\begin{list2}
\item[] Member of Data Days Scientific Group (\href {https://datadays.sharif.edu}{DataDays} - A Machine Learning and Data Science Competition) Sharif University of Technology \hspace*{\fill}\mbox{\textit {Nov 2019 - Mar 2020}}
\item[] Contestant of Webelopers (A web competition) Sharif University of Technology \hfill\textit{Oct 2019} 
\item[] Data Days Executive Staff, Sharif University of Technology \hfill\textit{Feb 2019} 
\item[] ACM Executive Staff, ACM-International Collegiate Programming Contest \hfill\textit{Dec 2018}
\item[] Sharif AI Executive Staff, Sharif Artificial Intelligence Challenge \hfill\textit{Mar 2018 and Mar 2019}
\end{list2}
   
 \vspace{-0.05in}
\section{\sc Languages} 
\begin{list2}
\item[] English (Fluent) 
\begin{list2}
		\item {\bf TOEFL : 109/120}
			
		Reading: 30/30, Listening: 30/30, Speaking: 26/30, Writing: 23/30
\end{list2}
\item[] Persian (Native)
%Reading: 29/30, Listening: 30/30, Speaking: 27/30, Writing: 26/30
%\item{\bf GRE}\\
%Verbal Reasoning: 152/170, Quantitative Reasoning: 163/170, Analytical Writing: 3.5/6
%\item[] Arabic (Intermediate)
\end{list2}


\end{resume}   
\end{document}